### 2023-04-27 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

\chapter{Methodology}
\label{chap:Metodology}

This chapter is about describing the methodology and developments to achieve the project goals. 
Firstly, let me begin by elaborating on the workings of the classification process in the processing thread. Moving on, I will then delve into the operational sequences of the controller thread. Lastly, I will provide an explanation on the implementation of the controller.

@@

\subsection{Statistical Analysis}
In Sjaaks\cite{Sjaaks} work, the author exposed some signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time domain and frequency domain analysis.
We acquire the current data frame of 0.5s and through statistical analysis in the signal such as mean value and standard deviation we apply in our automatic classification the relative standard deviation. Which is referred as the sample standard deviation divided by the sample mean values. Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks method.

@@

To classify the multi jet, after running many steps experiments as shown in figure \ref{fig:raw_data} I noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean. 
I also noticed that the cone jet current was almost fixed all its spectrum. 
This effect was cited by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.

With that, I implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
The cone jet current can be calculated by the scaling laws\ref{sec:scalling-laws} formula.
The value 1.14 was found by repeating a lot of experiments with the same liquid, but varying the flowrate and the voltage. This means this value is just defined for pure ethanol, the liquid used in all those experiments.
The classification in the algorithm was divided in three steps as shown below. The algorithm is shown in \ref{alg:statistical_class}.

@@

@@

@@

The map that will be explained below is the most relevant sequence in this work. This type of experiment saves human work and time, create a precise analysis and can be compared with previous works for validation of methodology.
The purpose is to map the operational window, seen in Figure \ref{fig:ganan_calvo_fig}, that can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration\cite{gananCalvo}.

    \begin{figure}[H]
        \center
        \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
        \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} . The window formed by these points is where the system operated in the stable cone-jet. Operational windows depend of the liquid and configuration setup. Different windows are represented for different liquid conductivity. The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
        \label{fig:ganan_calvo_fig}
    \end{figure}

To reach certain map it is necessary to traverse flow rate and voltage values acquiring samples.
The flow rate (X axis) and voltage (Y axis) values for each experiment can be configured in the setup.json file.
The algorithm for this sequence is a copy of the step sequence\ref{subsec:step_routine} for each flow rate chosen. It is illustrated in the algorithm \ref{alg:mapping_algorithm}.

>>>>

\chapter{Methodology}
\label{chap:Methodology}

This chapter is about describing the methodology and developments to achieve the project goals. 
Firstly, I begin by elaborating on the workings of the classification process in the processing thread. Moving on, I will then delve into the operational sequences of the controller thread. Lastly, I will provide an explanation on the implementation of the controller.

@@

\subsection{Statistical Analysis}
In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
We acquire the current data frame of 0.5s with 100 KHz as sampling frequency. With that each current sample as 50 thousand current values. Through statistical analysis in these values such as mean and standard deviation we apply in our automatic classification the relative standard deviation. Which is referred as the sample standard deviation divided by the sample mean values. 
Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks method.

@@

To classify the multi jet, after running many steps experiments as shown in figure \ref{fig:raw_data} I noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean. 
I also noticed that the cone jet current was almost fixed all its spectrum. 
These effects were exposed by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.

With that, I implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
The cone jet current can be calculated by the scaling laws\ref{sec:scalling-laws} formula.
The value 1.14 was found by repeating a lot of experiments with the same liquid, but varying the flow rate and the voltage. This means this value is just defined for pure ethanol, the liquid used in all those experiments.
The classification in the algorithm was divided in three steps as shown below. The algorithm is shown in \ref{alg:statistical_class}.

@@

The ramp sequence is simply done by sending one command to the power supply to perform a ramp in the voltage with initial, final and slope values.
The flow rate for this sequence is constant, and the experiment consists in a voltage range scan.

@@

The step sequence is done by the same command send to the power supply but with the maximum slope value in order to proximate of a step signal.
By waiting a certain defined \emph{step\_time} and repeating the command in a loop until it gets into the final voltage. This algorithm is represented in \ref{alg:stepping_algorithm}.

@@

The map that will be explained below is the most relevant sequence in this work. This type of experiment saves human work and time, create a precise analysis and can be compared with previous works for validation of methodology.
The purpose is to map the operational window, seen in Figure \ref{fig:map3Data_fig}, that can be defined where the spraying mode can be stabilized based on the flow rate, voltage and the setup configuration.

To reach certain map it is necessary to traverse flow rate and voltage values acquiring samples.
The flow rate (X axis) and voltage (Y axis) values for each experiment can be configured in the setup.json file.
The algorithm for this sequence is a loop of the step sequence\ref{subsec:step_routine} for each flow rate chosen. It is represented in the algorithm \ref{alg:mapping_algorithm}.

### 2023-04-27 Documentation/UFMG/PFCII/Results/Results.tex
documentation

>>>>

\begin{figure}[H]
    \center
    \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
    \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} . The window formed by these points is where the system operated in the stable cone-jet. Operational windows depend of the liquid and configuration setup. Different windows are represented for different liquid conductivity. The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
    \label{fig:ganan_calvo_fig}
\end{figure}
